---
title: "AD 699 Final Project"
author: "Team Boston Cream"
date: "2023-12-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(leaflet)
library(wordcloud)
library(textdata)
library(tidytext)
library(tm)
library(e1071)
```

```{r}
r <- read_csv('rome_listings.csv')
```

```{r}
mv <- r %>%
  filter(neighbourhood_cleansed == "XII Monte Verde")
```

```{r}
colSums(is.na(mv))
```

```{r S I I A}
mv1 <- select(mv, id, description, neighborhood_overview, host_id, host_name, host_since, host_response_time,
              host_response_rate, host_acceptance_rate, host_total_listings_count, host_has_profile_pic, 
              host_identity_verified, property_type, accommodates, amenities, price,
              minimum_nights, maximum_nights, has_availability, number_of_reviews, 
              review_scores_rating, instant_bookable)

missing_values <- colSums(is.na(mv1))
mvd <- data.frame(Variable = names(missing_values),
                  Missing_Count = missing_values) %>%
  filter(Missing_Count > 0)
mvd

summary(mv1$review_scores_rating)

m <-median(mv1$review_scores_rating, na.rm = TRUE)

mv1$description[is.na(mv1$description)] <- ""
mv1$neighborhood_overview[is.na(mv1$neighborhood_overview)] <- ""
mv1$review_scores_rating[is.na(mv1$review_scores_rating)] <- m

colSums(is.na(mv1))
```

S I I B: We first filter the original data frame so that it only contains our neighborhood and columns that are important for the purpose of this project. Then the output above shows that only description, neighborhood_overview, and review_scores_rating have missing values. For both description and neighborhood_overview, we replace na values with empty space. The reason for doing so is that na in general description usually means there the host write nothing in that section, which is the same as empty space. This is a better approach than just deleting the na rows becausse that means we will lose about 14% of our data which is not ideal. Also, we can still do text mining on these two variables since empty space does not change anything. For review_scores_rating,we first check the summary stats for that column and then decide that it is best to replace missing values with its median value. There do exist 0s for the score which lower its mean and we think median is a more accurate representation of the true average score here.

```{r S I II A}
mv1$price <- as.numeric(gsub("[\\$,]", "", mv1$price))

ss <- c(mean(mv1$price), median(mv1$price), min(mv1$price), max(mv1$price), sd(mv1$price))
ss_names <- c('mean', 'median', 'minimum', 'maximum', 'standard deviation')

df <- data.frame(metric = ss_names, value = ss)
df
```

S I II B: The variable we are interested is price. In order to do any analysis on it we first get rid of the dollar sign and convert the column into numeric. The five summary statistics we use here are mean, median, minimum, maximum, and standard deviation. The max price is 9999 which is much higher than the average, even compared to the top 5 highest price. There is a high chance that it is entered incorrectly, maybe it was supposed to be 99.99 instead of 9999. We need to check further on that specific row in order to make final conclusion.

Such high price also has a ribbling effect on the mean and standard deviation, which are 146 and 340. This does not make sense since that will mean any unit that is negative 1 standard deviation away from the mean price will have a negative price, which defies common sense. The median of the price is \$110 which is reasonable based on our domain knowledge for this area.

```{r S I III A}
# data cleanup and filtering
mv2 <- filter(mv1, review_scores_rating > 3.5) 
mv2$instant_bookable <- factor(mv2$instant_bookable)
mv2$host_response_time <- factor(mv2$host_response_time)
mv2$property_type <- factor(mv2$property_type)
mv3 <- mv2 %>% 
  mutate(rr = ifelse(host_response_rate == 'N/A', NA , as.numeric(sub("%", "", host_response_rate))),
        response_rate_category = cut(rr, breaks = c(0, 20, 40, 60, 80, 100, Inf), 
        labels = c("None", "Very Slow", "Slow", "Medium", "Fast", "Very Fast"), include.lowest = TRUE),
        days_being_host = as.numeric(today() - host_since))


# Graphs 
ggplot(mv3, aes(x = review_scores_rating)) + geom_histogram(binwidth = 0.1) + theme_minimal() + 
  labs(title = 'Histogram of Review Scores Rating') + theme(plot.title = element_text(hjust = 0.5))

ggplot(mv3, aes(x = review_scores_rating, y = number_of_reviews)) + geom_point() + theme_minimal() + 
  labs(title = 'Scatter Plot of Review Scores Rating') + theme(plot.title = element_text(hjust = 0.5))

cc <- c("None" = 'red', "Very Slow" = 'blue', "Slow" = 'yellow', 
        "Medium" = 'purple', "Fast" = 'black', "Very Fast" = 'green')
ggplot(mv3, aes(x = review_scores_rating, y = days_being_host, col = response_rate_category)) + 
  geom_point(size = 2, alpha = 0.5) + scale_color_manual(values = cc) + theme_minimal() +
  labs(title = 'Review Scores Rating by Response Rate and Host Length') + theme(plot.title = element_text(hjust = 0.5))

ggplot(mv3, aes(x = instant_bookable, y = review_scores_rating, fill = instant_bookable)) + geom_boxplot() + theme_minimal()+ labs(title = 'Box Plot of Review Scores Rating by Booking Convenience') + theme(plot.title = element_text(hjust = 0.5))

ggplot(mv3, aes(y = property_type, x = host_response_time, fill = review_scores_rating)) +
  scale_fill_gradient(low = "red", high = "lightgreen") + theme_minimal() + geom_tile() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(title = 'Heat Map of Review Scores Rating')
```
S I III B:
The variable we choose here is review_scores_rating. In order to make the graphs more readable, we filter out all the data with score below 3.5(they are outliers anyway and there are not so many of them). The first graph is a histogram shows the distribution of the rating. It seems like majority of the scores are from 4.4 to 5 with peak around 4.8, most of the hosts in our neighborhood have a good reputation. The second graph is a scatter plot of rating and number of reviews. Although the relationship between these two variables do not seem to be very linear, all the units that get 5 do not have that many reviews. Also, most of the units have under 100 reviews. 

The third graph is another scatter plot of rating based on response rate and host length. The majority of units that get 5 seem to response very fast. The slow and very slow response tend to get lower ratings, but not by much. Review scores rating also do not seem to be affected by how long the person has been a host. The forth plot is a box plot based on booking convenience. Suprisingly the units that are not instant bookable are getting slightly lower scores. This might be due to the potential lack of communication if a unit could be booked instantly. The last graph is a heat map with respect to response time and property type. We get a consistent result on how response time affect review scores, and we can also see that property type does not influence ratings that much, since there is a relatively high range of scores across all types. 


```{r S I IV}
m <- leaflet() %>% 
  addTiles() %>% 
  addCircles(lng= mv$longitude , lat= mv$latitude)

m 
```
S I IV:
The majority of properties are located in the actual neighborhood, which is what we expected. There is a higher density next to the Tevere river area. This makes sense because people will probably want to enjoy the view. There are also some properties that are located outside of the neighborhood and separated by the Grande Raccordo Anulare. From the map it seems like the landscapes are very different between these two areas. 

```{r S I V}
t <- select(mv, neighborhood_overview) %>%
  na.omit() %>%
  unnest_tokens(word, neighborhood_overview)
#  group_by(word) %>%
#  summarize(n = n())

swe <- data.frame(word = stopwords("en"), stringsAsFactors = FALSE) #Italian stop words
swi <- data.frame(word = stopwords("it"), stringsAsFactors = FALSE) #English stop words 
extra_sw <- data.frame(word = c('br', 'monteverde'))
sw <- rbind(swe, swi, extra_sw)
w <- anti_join(t, sw, by = "word")

wordcloud(words = w,  min.freq = 150,  scale = c(3.5, 0.5), max.words = 30)
```
S I V: Some of the key words are 'trastevere', 'quartiere', 'rome', and 'villa'. 

Step 2 Prediction
```{r}
library(dplyr)
library(forecast)
```
Step 2 Part 1 Task A
```{r S II I}
mv_mlr<-mv
missing_values <- sapply(mv_mlr, function(x) sum(is.na(x)))
missing_values <- sort(missing_values, decreasing = TRUE)
missing_values
sum(is.na(mv_mlr))
```
S II I A:
In the initial stage of the process, we preprocess the data to prepare it for a regression model, with 'price' as the dependent variable. Identifying true NA values throughout the data set is crucial and several variables exhibit NA counts exceeding 500. When we are dealing with these variables, even if the NAs are replaced with the mean, median, or mode, might be unnecessary and introduce uncontrolled effects. In order to mitigate overfitting or underfitting in our model, we opt to drop variables with more than 500 NA values. 

Some important variables, such as 'bedrooms' or 'review scores,' still have NA values. Variables like 'first review' or 'last review' are unrelated to our pricing model, so we eliminate them in a new data set. Then, we use the median to fill in the NA values for 'review_scores_rating,' 'reviews_per_month,' 'bedrooms,' and 'beds.'

```{r}
mv_mlr <- mv_mlr %>%
  select(-neighbourhood_group_cleansed, -bathrooms, -calendar_updated, 
         -license, -host_neighbourhood, -host_about, -neighborhood_overview, 
         -neighbourhood, -host_location, -review_scores_accuracy, 
         -review_scores_cleanliness, -review_scores_checkin, 
         -review_scores_communication, -review_scores_location, 
         -review_scores_value, -first_review, -last_review)

#Replace with median
mv_mlr$review_scores_rating <- ifelse(is.na(mv_mlr$review_scores_rating), 
                                                median(mv_mlr$review_scores_rating, na.rm = TRUE), 
                                                mv_mlr$review_scores_rating)

mv_mlr$reviews_per_month <- ifelse(is.na(mv_mlr$reviews_per_month), 
                                             median(mv_mlr$reviews_per_month, na.rm = TRUE), 
                                             mv_mlr$reviews_per_month)

mv_mlr$bedrooms <- ifelse(is.na(mv_mlr$bedrooms), 
                                    median(mv_mlr$bedrooms, na.rm = TRUE), 
                                    mv_mlr$bedrooms)

mv_mlr$beds <- ifelse(is.na(mv_mlr$beds), 
                                median(mv_mlr$beds, na.rm = TRUE), 
                                mv_mlr$beds)

mv_mlr$price <- gsub("\\$", "", mv_mlr$price) 
mv_mlr$price <- gsub(",", "", mv_mlr$price)   
mv_mlr$price <- as.numeric(mv_mlr$price)

mv_data <- mv_mlr %>%
  select(price, room_type, accommodates, bedrooms, beds, 
         host_is_superhost, review_scores_rating, number_of_reviews, 
         availability_365, instant_bookable)
str(mv_data)


mv_data$host_is_superhost <- ifelse(mv_data$host_is_superhost == "TRUE", 1, 0)
mv_data$instant_bookable <- as.numeric(mv_data$instant_bookable)  


dummy_room_type <- model.matrix(~ room_type - 1, data = mv_data)
dummy_room_type <- dummy_room_type[, -4]
mv_data <- cbind(mv_data, dummy_room_type)
mv_data <- mv_data %>% dplyr::select(-room_type)

mv_data$log_price <- log(mv_data$price)
variables_to_scale <- c("number_of_reviews", "availability_365")
mv_data[variables_to_scale] <- scale(mv_data[variables_to_scale])
```
S II I A:
Additionally, we notice irrelevant variables like scraping time and URLs in a significant part of the data set. These variables are excluded from our linear regression analysis. We select the following variables for our model: 'price,' 'room_type,' 'accommodates,' 'bedrooms,' 'beds,' 'host_is_superhost,' 'review_scores_rating,' 'number_of_reviews,' 'availability_365,' and 'instant_bookable.' Although 'availability_365' and 'instant_bookable' might intuitively correlate with price, we retain them in the first phase. 'host_is_superhost' indicates a host's popularity and extra services, potentially having an indirect relationship with the price. Furthermore, 'review_scores_rating' and 'number_of_reviews' reflect the property's popularity, influencing price dynamics.

Next, we transform the character variable into a numeric format, removing the '$' sign and retaining only the numeric string in the values. A log transformation is then applied to the price variable to mitigate the effects of outliers, especially in larger transaction.

```{r}
str(mv_data)
mv_data<- na.omit(mv_data)
sum(is.na(mv_data))
```
Model evaluation involves several metrics such as R-squared, RMSE, and MAE for both training and validation. A reasonable R-squared is prioritized over a simple high R-squared. A 0.05 p-value is used for further tuning to ensure the precision of the model and check the relationship between predicting variables and the dependent variable, price.

```{r}
library(corrplot)
cor_matrix <- cor(mv_data)
# Create a correlation plot
corrplot(cor_matrix, method = "color", type = "upper", tl.col = "black", tl.srt = 45,number.cex = 0.7)
```
```{r}
mv_data1 <- mv_data[, !colnames(mv_data) %in% c("accommodates", "room_typePrivate room")]
cor_matrix1 <- cor(mv_data1)
# Create a correlation plot
corrplot(cor_matrix1, method = "color", type = "upper", tl.col = "black", tl.srt = 45,number.cex = 0.7)
```
S II I A:
Before fitting all variables into the model, we check for collinearity among them using a correlation plot. A correlation higher than 0.6 is considered significant. From the plot, we observe high correlations among 'accommodates' and 'beds,' 'accommodates' and 'bedrooms,' and 'room_typePrivate room' and 'room_type entire room.' Consequently, we decide to exclude 'accommodates' and 'room_typePrivate room,' resulting in no high correlation in our price model.

Step 2 Part 1 Task B
```{r}
set.seed(699)
train.index <- sample(c(1:nrow(mv_data1)), nrow(mv_data1)*0.59)

# Split the data into training and validation sets
train.df <- mv_data1[train.index, ]
valid.df <- mv_data1[-train.index, ]

model <- lm(log_price ~ . - price, data = train.df)
# Summary of the model
summary(model)
```
S II I B:
We have our final MLR model and its summary shown in the table above. The whole equation is describe as: 3.77929(intercept)+0.27113* bedrooms+0.03728* beds+0.01825* host_is_superhost+0.03091* number_of_reviews-0.07905* number_of_reviews+ 0.12548* availability_365+0.17953* instant_bookable+0.26160* room_typeEntire home/apt+ 0.29225* room_typeHotel room

In the model, bedrooms, beds, number_of_reviewsand availability_365 are numerical variables which number_of_reviews and availability_365 are both scaled to make the model less overfitting. The rest are binary values which are transferred from categorical variables. 

The regression summary reveals some variables with higher p-values than our threshold of 0.05. 'host_is_superhost,' 'review_scores_rating,' and 'room_typeHotel room' are not statistically significant to the dependent variable 'price.' Notably, 'bedrooms' has a coefficient of 0.271, aligning with the intuitive understanding that more rooms impact pricing. Surprisingly, 'number_of_reviews' is associated with a decrease in price.we have Multiple R-squared:  0.371 is close enough for our estimate since it is a raw data with a lot of missing variables. A high r squared would result in overfitting problem.


```{r}
backward <- step(model, direction='backward', scope=formula(model), trace=0)
summary(backward)
```
We perform backward elimination in oder to remove predictors with the highest p-values results in the exclusion of 'host_is_superhost,' 'review_scores_rating,' and 'room_typeHotel room.' This slightly increases R-squared but has minimal impact on adjusted R-squared.

Step 2 Part 1 Task C
```{r}
train_predictions <- exp(predict(backward, newdata=train.df))
valid_predictions <- exp(predict(backward, newdata=valid.df))

# Assess accuracy for training set with original price scale
train_accuracy <- accuracy(train_predictions, train.df$price )
train_accuracy 

# Assess accuracy for test set with original price scale
valid_accuracy <- accuracy(valid_predictions, valid.df$price)
valid_accuracy
```
S II I C:
Further performance analysis indicates a mean error of 21.73 on the training set, suggesting a slight overprediction tendency. The RMSE and MAE values are 251.65 and 55.08, respectively. On the test set, the model shows a mean error of 43.48, higher RMSE (427.85) and MAE (71.64), with a lower MPE (-4.86%) and a similar MAPE (37.13%). These results signal a need for refinement to enhance predictive accuracy, especially on unseen data.


Step 3 Classification
Step 3 Part 1 Task A
```{r}
mv$price <- as.numeric(gsub("[\\$,]", "", mv$price))
#extract beds and bedrooms
pattern_bedrooms <- ".*?(\\d+)\\s*bedroom.*"
pattern_beds <- ".*?(\\d+)\\s*beds.*"
mv$number_of_bedrooms <- as.numeric(gsub(pattern_bedrooms, "\\1", mv$name, perl = TRUE))
mv$number_of_beds <- as.numeric(gsub(pattern_beds, "\\1", mv$name, perl = TRUE))

# Replace NA with 0 if needed (assuming no mention means 0)
mv$number_of_bedrooms[is.na(mv$number_of_bedrooms)] <- 0
mv$number_of_beds[is.na(mv$number_of_beds)] <- 0
contains_one_bed <- grepl("1 bed", mv$name)
mv$number_of_beds[contains_one_bed]<-1
mv_bed<-mv%>%select(name,number_of_bedrooms,number_of_beds)
```

```{r}
knn_df <- mv %>% select(c('amenities', 'price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms'))

colSums(is.na(knn_df))


condition <-grepl('kitchen', knn_df$amenities, ignore.case=TRUE)
knn_df$amenities <- as.integer(condition)
knn_df$amenities <- as.factor(knn_df$amenities)

set.seed(699)
train.index <- sample(c(1:nrow(knn_df)), nrow(knn_df)*0.6)
train.df <- knn_df[train.index, ]
valid.df <- knn_df[-train.index, ]

class_0 <- filter(train.df, amenities==0)
class_1 <- filter(train.df, amenities==1)

t.test(class_0$price, class_1$price)
t.test(class_0$accommodates, class_1$accommodates)
t.test(class_0$number_of_bedrooms, class_1$number_of_bedrooms)
t.test(class_0$number_of_beds, class_1$number_of_beds)
t.test(class_0$calculated_host_listings_count_private_rooms, class_1$calculated_host_listings_count_private_rooms)
t.test(class_0$calculated_host_listings_count_shared_rooms, class_1$calculated_host_listings_count_shared_rooms)

library('caret')
train.norm.df <- train.df
valid.norm.df <- valid.df
norm.values <- preProcess(train.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')],
                          method=c('center', 'scale'))
train.norm.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')] <-
  predict(norm.values, train.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')])
valid.norm.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')] <-
  predict(norm.values, valid.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')])

library('FNN')
accuracy.df <- data.frame(k=seq(1, 14, 1), accuracy = rep(0, 14))

for (i in 1:14) {
  knn.pred <- knn(train.norm.df[,c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')], valid.norm.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')],
 cl= train.norm.df$amenities , k=i)
  
  accuracy.df[i,2] <- confusionMatrix(knn.pred, valid.norm.df$amenities)$overall[1]
}
accuracy.df


ggplot(accuracy.df, aes(x=k, y=accuracy)) + 
  geom_point(color="blue") + 
  geom_line(color="blue", aes(group=1)) + 
  ggtitle("Accuracy vs. k values") + 
  xlab("k values") + 
  ylab("Accuracy")

  knn.pred <- knn(train.norm.df[,c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')], valid.norm.df[, c('price', 'accommodates', 'number_of_bedrooms', 'number_of_beds'
                          , 'calculated_host_listings_count_private_rooms', 'calculated_host_listings_count_shared_rooms')],
 cl= train.norm.df$amenities , k=3)

confusionMatrix(knn.pred, valid.norm.df$amenities, positive = '1')
```
Step III: Classification Part I B: 
To begin with, we start thinking of the target variable which is amenities. The amenities column contains all unique value which is hard to predict for any model. Thus, we decide to choose kitchen as the outcome class since having a own kitchen is usually the signal of luxury and big apartments. 

After dealing with outcome classes, feature selection becomes our priority. Since K nearest neighbor is distance-based model, numeric inputs are the only type that is acceptable under this model. Six features that seems to be logical for predicting luxury apartments were our first choice. After implementing t test of each of those features, all six features are left with contributions to the predictive power. Moreover, we used the above process to find and plot the best k for our model. It turns out that 3 is the best k parameter. According to the confusion matrix of the knn model, the accuracy is 89.1% which is relatively good here. In addition, the TPR is 96% which shows a perfect performance of predicting positive class.  

Step 3 Part 2 Task A
```{r}
mv_nb<-mv %>% select(review_scores_rating,host_is_superhost,host_response_time,host_acceptance_rate,room_type)
mv_nb<-subset(mv_nb, !is.na(host_is_superhost))
breaks_mam <- quantile(mv_nb$review_scores_rating, probs = seq(0, 1, 1/3), na.rm = TRUE)
mv_nb$review_scores_rating<-cut(mv_nb$review_scores_rating,breaks=breaks_mam,
                              labels = c("low","mid","high"),
                              include.lowest = TRUE)
mv_nb$review_scores_rating <- factor(mv_nb$review_scores_rating, levels = c(levels(mv_nb$review_scores_rating), "NA_cate"))
mv_nb$review_scores_rating[is.na(mv_nb$review_scores_rating)] <- "NA_cate"
mv_nb$host_acceptance_rate[mv_nb$host_acceptance_rate == "N/A"] <- 0
mv_nb$host_acceptance_rate <- as.numeric(gsub("[^0-9.]", "", mv_nb$host_acceptance_rate))
mv_nb$host_acceptance_rate<-mv_nb$host_acceptance_rate/100
breaks_host <- quantile(mv_nb$host_acceptance_rate, probs = seq(0, 1, 1/2), na.rm = TRUE)
mv_nb$host_acceptance_rate<-cut(mv_nb$host_acceptance_rate,breaks=breaks_host,
                              labels = c("low","high"),
                              include.lowest = TRUE)
mv_nb$host_is_superhost<-as.factor(mv_nb$host_is_superhost)
mv_nb$host_response_time<-as.factor(mv_nb$host_response_time)
mv_nb$room_type<-as.factor(mv_nb$room_type)
set.seed(699)
train_prop<-0.6
train.index<-sample(c(1:nrow(mv_nb)),nrow(mv_nb)*train_prop)
train.fit<-mv_nb[train.index,]
valid.fit<-mv_nb[-train.index,]
fitnb<-naiveBayes(review_scores_rating~.,data=train.fit)
fitnb
```
In order to make a Naïve Bayes model to predict the review score rating for each house, three equal frequency bins were applied to review_score_rating variables to assign three groups for the variable, which were low, mid, and high that represent low review rating, mid-level rating, and high rating. Then, features such as whether the host is a super host, time the host take a response, the acceptance rate, and the room type were chosen to predict the review score rating because a host service to customers can play a important role in affecting customers rating to the house. It is also important that the type of the house can affect the living experience of customers. Therefore, these variables can help in determining the level of review rating for Airbnb houses.


Step 3 Part 2 Task B
```{r}
fakehouse<-data.frame(
  host_is_superhost="TRUE",
  host_response_time="within an hour",
  host_acceptance_rate="high",
  room_type="Private room"
)
prediction <- predict(fitnb, fakehouse)
prediction
```
The fictional person is a superhost with a response time within an hour, high acceptance rate, and listing private room. The model predict that this person will receive mid-level review score.

Step 3 Part 2 Task C
```{r}
fitnb
train_predictions <- predict(fitnb, train.fit)
validation_predictions <- predict(fitnb, valid.fit)
train_cm <- table(Predicted = train_predictions, Actual = train.fit$review_scores_rating)
validation_cm <- table(Predicted = validation_predictions, Actual = valid.fit$review_scores_rating)
train_accuracy <- sum(diag(train_cm)) / sum(train_cm)
validation_accuracy <- sum(diag(validation_cm)) / sum(validation_cm)

```
```{r}
train_accuracy
validation_accuracy
```
S III II D:
After the model is conducted and tested, the performance was assessed by accuracy rate. Based on the model performance, the train set had an accuracy rate of 0.4274 while the validation set had an accuracy rate of 0.4268. The difference between in accuracy rate between train set and validation set is similar, which suggests that there are no potential overfitting problems.

It is also important that since the outcome variable is mostly evenly distributed, a naive model that always predicts the most common class would have an accuracy of about 25%. In this case, a 43% accuracy would be significantly better than the baseline.


Step 3 Part 3 
```{r}
#tree model
library(rpart)
library(rpart.plot)

tree_df <- mv%>% select('instant_bookable', 42:49, 52:55)

tree_df$instant_bookable <- as.factor(tree_df$instant_bookable)

set.seed(699)
train.index <- sample(c(1:nrow(tree_df)), nrow(tree_df)*0.6)
train.df <- tree_df[train.index, ]
valid.df <- tree_df[-train.index, ]

tree <- rpart(instant_bookable~., data=train.df, method= 'class')
rpart.plot(tree, type = 4, extra = 3)
printcp(tree)
```
Classification, Part III B: Based on the cp table above, we decide to implement cp of 0.010582 with minsplit of 11 since it produces the lowest x error here.
Classification, Part III C: Here is the graph of our tree.

```{r}
new_tree <- rpart(instant_bookable~., data=train.df, method = 'class',
                  cp=0.010582, minsplit=11)

rpart.plot(new_tree, type = 1, extra = 3)

prediction_of_my_tree_train <- predict(new_tree, train.df, type='class')
cf_tree_train <- confusionMatrix(prediction_of_my_tree_train, train.df$instant_bookable, positive = 'TRUE')
print(cf_tree_train)

prediction_of_my_tree_valid <- predict(new_tree, valid.df, type='class')
cf_tree_valid <- confusionMatrix(prediction_of_my_tree_valid, valid.df$instant_bookable, positive = 'TRUE')
print(cf_tree_valid)
```
Classification, Part III D: 
We start our modeling process by searching for inputs that might seem logic in predicting whether it is instantly bookable or not. We decide to take all the variables that are related to availability and nights as inputs here. After cross-validation, we implement those best hyper parameters for the tree model and refit the data as needed. The tree automatically locates the most important feature here which is minimum minimum nights based on the graph above. According to the confusion matrix above, the model has an accuracy of 0.65 and TPR rate of 0.57 which is relative feasible for predicting. 

Step 4 Cluster 
Step 4 Task A and B
```{r}
mv_cluster<- select(mv,id,number_of_beds,price)
sum(is.na(mv_cluster))
mv_cluster$price <- as.numeric(gsub("[\\$,]", "", mv_cluster$price))
```

```{r}
mv_cluster$id<-as.character(mv_cluster$id)
mv_cluster<-as.data.frame(mv_cluster)
row.names(mv_cluster)<-mv_cluster[,1]
mv_cluster<-mv_cluster[,-1]
mv_cluster_norm<-sapply(mv_cluster,scale)
d.norm<-dist(mv_cluster_norm,method="euclidean")
km<-kmeans(mv_cluster_norm,4)
mv_cluster$cluster <- as.factor(km$cluster)
ggplot(mv_cluster,aes(x=number_of_beds,y=price,color=cluster))+geom_point()
```

```{r}
set.seed(699)
mv_cluster_norm<-as.data.frame(mv_cluster_norm)
mv_cluster_norm$price<-mv_cluster_norm$price*2
d.norm<-dist(mv_cluster_norm,method="euclidean")
km<-kmeans(mv_cluster_norm,4)
mv_cluster$cluster <- as.factor(km$cluster)
ggplot(mv_cluster,aes(x=number_of_beds,y=price,color=cluster))+geom_point()
```

```{r}
mv_cluster$cluster<- ifelse(mv_cluster$cluster == 1, "More Bed Normal Price",
                          ifelse(mv_cluster$cluster == 2, "High End House",
                                 ifelse(mv_cluster$cluster == 3, "Normal Bed Normal Price","Luxury")))
```
For cluster analysis, two variables, number of bed and price, were chosen to cluster all Airbnb houses to 4 different clusters. The reason why these two variables were chosen is that for a customer who wants to book a house, the two main factors that affect decision making are how many people the house can serve and how much price they need to pay. Thus, the number of beds and price of the house are the essential variables that affect customer's decision making and were chosen to differentiate clusters.

The method of clustering used is k-means cluster. Since values of price variable are much higher than number of beds, normalization of variables was conducted to remove the effect of big numbers. The initial clustering was not successful because 4 different clusters are mainly based on number of beds rather than both beds and prices. Therefore, the weight of price was doubled to find out if there is any change. The result of double weighted price shows a good result that distinguish different clusters by both beds and price.

The four different clusters were given the following names, high end house, luxury, more bed normal price, and normal bed normal price. High end house represents houses that have higher prices. Luxury represents houses that charge extremely high prices for just 1 night. More bed normal price represents houses that have more than 3 beds with normal price. Normal bed normal price represents houses that have about 0 to 2 beds with normal price.

Step 4 Part 3
```{r}
ggplot(mv_cluster,aes(x=cluster,y=price))+geom_boxplot()
mv_cluster_nol<-mv_cluster %>% filter(cluster !="Luxury")
ggplot(mv_cluster_nol,aes(x=cluster,y=price))+geom_boxplot()
```
From the box plot of prices, it is noticeable that Luxury house charges extremely high prices that even above $7500 per night, while other houses charge a lower price. By removing the outliers from the luxury house, high end house typically charges price that is about $500, while the remaining three clusters charge prices range from $100 to $200.

```{r}
ggplot(mv_cluster,aes(x=number_of_beds,fill=cluster))+geom_histogram(bins=50)
```
From the histogram of beds, it is obvious that Normal number bed houses have number of beds around 0-3. More number bed houses have number of beds more than 3. For Luxury houses, number of beds seems not affect the price. The number of beds range from 2 to 5. For high end houses, the number of beds range from 1 to over 10.

```{r}
ggplot(mv_cluster,aes(x=cluster,y=number_of_beds))+geom_violin()
```
To have a clearer look about the number of beds shown in the data set, a violin plot is also generated. It can be found that for high end houses, the number of beds range from 1 to 12, while other clusters demonstrate the similar outcomes compared to the histogram.



Step V Conclusion:

The data preparation and exploration process is crucial for the rest of the project. It is good to check what each column contains, their data type, and if there are any redundancy or inter-dependency.  For example, the URL columns will not help with data analysis and there are many columns that all contain the bedroom/bed number information in our case, which can be taken out to make the future process easier. For property rental companies like Airbnb, it is also important to reflect on whether tracking certain metrics are necessary, since it does cost resource to do so and might turn out to be a waste. 

Many advertising/travel agency companies can really take advantage of the clustering models to feed customers more valuable information. For example, whenever there is a new customer start the vacation planning process, the agency can let them take a survey first. The survey will contain questions about key topics/metrics. Companies then use this result to place that customer into a certain cluster and start with item recommendations from that cluster. The company can also show the customer reviews from others in the same cluster, as "see those who are similar to you also says".   

This project also inspires us on how to deal with missing values within the data set in the future. The Naive Bayes classification part is a great example. The company can use other historical data to simply "predicting" the missing value as a alternative solution to using mean/median/mode. On top of that, the company can also change the target variable from a specific number to a categorical range in order to improve its accuracy by using this method. For example, instead of predicating a numeric value for the price, they can divide the result into low, medium, and high and give one of these three as result. 
